Forecasting the 2024 U.S. Presidential Election: An Analysis of Battleground States

### 2024-11-04 paper/paper.qmd
render pdf

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modsum1
#| fig-cap: 'Model summaries for Kamala Harris and Donald Trump at the national level using polling data.'

# Load and display the saved PNG
knitr::include_graphics(here("other", "graphs", "sum1.png"))

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modsum2
#| fig-cap: 'Model summary of Donald Trump’s support trends across key battleground states.'

# Load and display the saved PNG
knitr::include_graphics(here("other", "graphs", "sum2.png"))
```
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modsum3
#| fig-cap: 'Model summary of Kamala Harris’s support trends across key battleground states.'

# Load and display the saved PNG
knitr::include_graphics(here("other", "graphs", "sum3.png"))
```
